Gravitational field calculation in spherical coordinates using variable densities in depth

### 2019-03-08 manuscript/manuscript.tex
Replace "linear density" for "straight line"
On the density-based discretization algorithm we use a "straight line"
for computing the new discretization depth (if it's needed).
Naming this "straight line" as "linear density" could cause confusions
with the "linear density" used in the ratii determinations and may
induce readers to think that we are applying a piecewise linear
approximation of the density function.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]
    {figures/density-based-discretization-algorithm.pdf}
\caption{
    Example application of the density-based discretization algorithm to a non-linear
    density function.
    (a)~The normalised density function $\rho_n(r')$ (blue), current boundaries of the
    tesseroid (orange dots), and the linear density function $\rho_l(r')$ (orange line).
    The dashed red line represents the maximum density difference $\Delta \rho (r')$ at
    which the tesseroid would be divided (assuming that the
    inequality~\ref{eq:delta-density} is not satisfied).
    (b)~Second iteration of the algorithm with a new linear density function and maximum
    density difference. The tesseroid would be divided at the depth indicated by the
    dashed red line.
    (c)~Third iteration of the algorithm.
    (d)~Final output of the density-based discretization, assuming that all four new
    tesseroids satisfy inequality~\ref{eq:delta-density}.
}
\label{fig:density-discretization-algorithm}
\end{figure*}

@@

\textit{Step 1}:
Define a linear function $\rho_l(r')$ that assumes the same values as the normalised
density function $\rho_n(r')$ at the boundaries of the tesseroid ($r_1$ and $r_2$):

@@

\textit{Step 2}:
Evaluate the normalized and linear density functions on a range of $N$ radii between
$r_1$ and $r_2$.
We have opted for $N = 101$ but the specific value of $N$ is not critical to the
algorithm.

\textit{Step 3}:
Compute the absolute difference between the values of the linear and normalised density
functions:

>>>>

\begin{figure*}
\centering
\includegraphics[width=\linewidth]
    {figures/density-based-discretization-algorithm.pdf}
\caption{
    Example application of the density-based discretization algorithm to a non-linear
    density function.
    (a)~The normalised density function $\rho_n(r')$ (blue), current boundaries of the
    tesseroid (orange dots), and the straight line $\rho_l(r')$ (orange line).
    The dashed red line represents the maximum density difference $\Delta \rho (r')$ at
    which the tesseroid would be divided (assuming that the
    inequality~\ref{eq:delta-density} is not satisfied).
    (b)~Second iteration of the algorithm with a new straight line and maximum
    density difference. The tesseroid would be divided at the depth indicated by the
    dashed red line.
    (c)~Third iteration of the algorithm.
    (d)~Final output of the density-based discretization, assuming that all four new
    tesseroids satisfy inequality~\ref{eq:delta-density}.
}
\label{fig:density-discretization-algorithm}
\end{figure*}

@@

\textit{Step 1}:
Define a straight line $\rho_l(r')$ that assumes the same values as the normalised
density function $\rho_n(r')$ at the boundaries of the tesseroid ($r_1$ and $r_2$):

@@

\textit{Step 2}:
Evaluate the normalized density function and straight line on a range of $N$ radii
between $r_1$ and $r_2$.
We have opted for $N = 101$ but the specific value of $N$ is not critical to the
algorithm.

\textit{Step 3}:
Compute the absolute difference between the values of the straight line and the
normalised density function:
